---
title: "Apple Statistics"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First

[**7/30/20:applegraphs.R**](../R/applegraphs.R): I cleaned up the graphs by making more aesthetically pleasing plots, as well as producing plots with linear regression lines. 

```{r applegraphs}
source("../R/applegraphs.R")
ggplot(data = income2, mapping = aes(x = Fiscal.period, y = Total.Revenues, color = factor(Total.Revenues))) +
  geom_point(size = 3)
```

This first plot simply graphs total revenues against fiscal period. From a closer scope, the data seems to grow exponentially up until 2012, where it oscillates around a linear line. 

```{r applegraphs2}
source("../R/applegraphs.R")
ggplot(data = income2, mapping = aes(x = Fiscal.period, y = Total.Revenues, color = Total.Revenues)) +
  scale_shape_identity() +
  geom_point(size = 3) + 
  geom_smooth(method = "lm", aes(fill = Total.Revenues))
```

The second plot graphs the linear regression line on the data. From a larger scope, it becomes apparent that the data is relatively linear and that the regression line represents the data well. This indicates that the correlation coefficient is most likely positive and close to 1. The coefficient of determination also most likely is close to one, as a high percentage of data can be accounted for by the line of regression: looking at the shaded region, only a few points do not fall within the area (this is the 95% confidence interval).

```{r applegraphs3}
source("../R/applegraphs.R")
ggplot(data = income3, mapping = aes(x = Fiscal.period, y = Gross.Profit, color = factor(Gross.Profit))) +
  geom_point(size = 3)

ggplot(data = income3, mapping = aes(x = Fiscal.period, y = Gross.Profit, color = Gross.Profit)) +
  scale_shape_identity() +
  geom_point(size = 3) + 
  geom_smooth(method = "lm", aes(fill = Gross.Profit))
```

I then did the same with gross profit. The trends are very similar, so the same commentary that I made for total revenues similarly applies to gross profit. This isn't surprising, as gross profit and total revenues undoubtedly rise and fall together as they are very similar in theory.

## Second

[**7/31/20:applegraphs2.R**](../R/applegraphs2.R): I transformed the scatter plots of total revenues and gross profit with log transform (log10).

```{r applegraphs5}
source("../R/applegraphs2.R")
p + scale_x_log10() + scale_y_log10()

q + scale_x_log10() + scale_y_log10()
```

I then converted the scatter plots into bar plots, making it aesthetically pleasing with the colors and outline.

```{r applegraphs4}
source("../R/applegraphs2.R")
ggplot(income2, aes(x = Fiscal.period, y = Total.Revenues)) +
  geom_bar(stat = "identity", color = "blue", fill = rgb(0.2,0.6,0.8,0.7))

ggplot(income3, aes(x = Fiscal.period, y = Gross.Profit)) +
  geom_bar(stat = "identity", color = "purple", fill = rgb(.6, .6, 1, .7))
```

This first bar plot graphs total revenues against fiscal period, and the second graphs gross profit. The trend is, obviously, the same as with the scatter plots.