---
title: "Research Paper"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First

[**9/1/20:figure4d.R**](../R/figure4d.R)
I was selected for this research opportunity after demonstrating extraordinary work and dedication in my highly selective internship.

In this research project, I learned about the key gene (androgen receptor, AR) that regulates gene expression in prostate cancer. In previous studies, a set of AR target genes had been identified by high throughput technology. In our study, those genes classify patients into five groups by molecular subtypes, clinical features, and treatment responses using a patient cohort. I applied the same gene signatures to an independent cohort and validated the discoveries. 

Here, I utilized my newly acquired R analyses skills to obtain data from public databases (Gene Expression Omnibus, GEO) analyzed the data, and produced publishable graphics.

The annotations and steps are all within the R file.

```{r figure4d}
source("../R/figure4d.R")
```