---
title: "R Functions"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## First

**7/6/20:first.R**: My first script starts with 3 simple functions. First, I simulated the rolling of a pair of dice and the computation of their sum by writing a function dubbed `roll()`. This was executed using `sample()`. The next two functions essentially follow the same format. I took equations from my science classes in school and wrote them as functions. The gist of these two functions is that given the input values, it can calculate the result by following the given equation.
```{r first}
source("../R/first.R")
newton1 <- function(m, a) {
  f = m * a 
  f
}
newton1(m = 5, a = 3)
```

## Second

**7/7/20:Science.R**: This script is an expansion on the science equations in first.R. By utilizing the `uniroot()` function, my code can calculate any missing variable in the equation, given that the other parameters are inputed. This is done by giving `uniroot()` an interval to search for the answer. In order to ensure that all realistic values and answers can be produced, I set an extremely large interval: `c (-100000, 100000)`, or `c(0, 100000)` (for mass). I eliminated `delt` from the original function so that this function can solve for `t1` or `t0`.
```{r science}
source("../R/science.R")
newton2 <- function(f, m, a) {
  
  f1 <- function(x, m, a) x - m * a
  
  if(missing(f)) 
    return(uniroot(f1, c(-100000, 100000), m = m, a = a)$root)
  
  if(missing(m)) 
    return(uniroot(f1, c(0, 100000), x = f, a = a)$root)
  
  if(missing(a)) 
    return(uniroot(f1, c(-100000, 100000), x = f, m = m)$root)
}
newton2(f = 5, a = 3)
```